### 2019-08-14 paper_00_fluiddyn_meta/article.tex
Formatting equations
Proof read swe paper

\item \fluidpack{fft}~\cite[see the companion paper][]{fluidfft}: a package which
provides C++ and Python classes unifying various libraries to perform Fast Fourier
Transform (FFT) in sequential and in parallel.

\item \fluidpack{sim}~\cite[see the companion paper][]{fluidsim}: Numerically
oriented framework to run sequential and parallel Computational Fluid Dynamics
(CFD) simulations and on-the-fly post-processing for a variety of problems
(Navier-Stokes, Shallow Water, F\"oppl von K\'arm\'an equations, to name a few).
A study using \fluidpack{sim} has just been published in Physics of Fluids
\cite[]{LindborgMohanan2017}.

\item \fluidpack{lab}: Package to handle laboratory experiments. Primarily used to
communicate with various hardware devices such as motors and pumps, to handle I/O
between sensors, and to store data.
%
Experiments using \fluidpack{lab} have been carried out in the DAMTP fluid
laboratory \cite[Cambridge,
UK. cf.][]{LeclercqPartridgeAugierDalzielKerswell2016}, in ENS Lyon laboratory
\cite[Lyon, France,][]{salort2018} and at LEGI \cite[Grenoble,
France,][]{ISSF2016}.

\item \fluidpack{image}: Scalable image processing package which implements
various algorithms to calibrate cameras, to preprocess images, to do Particle
Image Velocimetry (PIV) and to postprocess data.
%
\fluidpack{image} is used to process images taken during experiments performed in the
Coriolis platform at LEGI \cite[]{ISSF2016}.

@@

\item \fluidpack{coriolis}: Small package used to carry out experiments in the
\href{http://www.legi.grenoble-inp.fr/web/spip.php?article757}{Coriolis platform}
(a large rotating platform participating in the European consortiums Euhit and
Hydralab) and open the data obtained \cite[see, for example,][]{ISSF2016}. One of
the motivations behind creating this package is to study how to use open-source to
create and share open-data.

@@

A detailed presentation on the above packages can be found in their respective
documentations on the web and for \fluidpack{fft} and \fluidpack{sim} in the
two companion papers \cite[]{fluidfft, fluidsim}.
%
The code base was designed to follow Python 2.7 syntax during its genesis. Now,
it has been made forward compatible with Python 3 through the use of external
package \pack{future}.
%
We now tend to abandon Python 2.7 support for the next releases of the package.
%
This article will now focus on the base package \fluiddyn.

\subsection{of the Python library \fluiddyn}

@@

\fbox{%
\begin{minipage}{\textwidth}
  \codeinline{%
    (im1\_1.png, im1\_2.png, im1\_3.png, im2\_1.png, im2\_2.png, im2\_3.png)}
\end{minipage}
}

@@

\fbox{%
\begin{minipage}{0.5\textwidth}
\codeinline{((im1\_1.png, im1\_2.png, im1\_3.png),\\
  (im2\_1.png, im2\_2.png, im2\_3.png))}\\
\end{minipage}
}
\fbox{%
\begin{minipage}{0.47\textwidth}
\codeinline{((im1\_1.png, im2\_1.png),\\
  (im1\_2.png, im2\_2.png),\\
  (im1\_3.png, im2\_3.png))}
\end{minipage}
}

>>>>

\item \fluidpack{fft}~\citep[see the companion paper][]{fluidfft}: a package which
provides C++ and Python classes unifying various libraries to perform Fast Fourier
Transform (FFT) in sequential and in parallel.

\item \fluidpack{sim}~\citep[see the companion paper][]{fluidsim}: Numerically
oriented framework to run sequential and parallel Computational Fluid Dynamics
(CFD) simulations and on-the-fly post-processing for a variety of problems
(Navier-Stokes, Shallow Water, F\"oppl von K\'arm\'an equations, to name a few).
A study using \fluidpack{sim} has just been published in Physics of Fluids
\citep[]{LindborgMohanan2017}.

\item \fluidpack{lab}: Package to handle laboratory experiments. Primarily used to
communicate with various hardware devices such as motors and pumps, to handle I/O
between sensors, and to store data.
%
Experiments using \fluidpack{lab} have been carried out in the DAMTP fluid
laboratory \citep[Cambridge,
UK. cf.][]{LeclercqPartridgeAugierDalzielKerswell2016}, in ENS Lyon laboratory
\citep[Lyon, France,][]{salort2018} and at LEGI \citep[Grenoble,
France,][]{ISSF2016}.

\item \fluidpack{image}: Scalable image processing package which implements
various algorithms to calibrate cameras, to preprocess images, to do Particle
Image Velocimetry (PIV) and to postprocess data.
%
\fluidpack{image} is used to process images taken during experiments performed in the
Coriolis platform at LEGI \citep[]{ISSF2016}.

@@

\item \fluidpack{coriolis}: Small package used to carry out experiments in the
\href{http://www.legi.grenoble-inp.fr/web/spip.php?article757}{Coriolis platform}
(a large rotating platform participating in the European consortiums Euhit and
Hydralab) and open the data obtained \citep[see, for example,][]{ISSF2016}. One of
the motivations behind creating this package is to study how to use open-source to
create and share open-data.

@@

A detailed presentation on the above packages can be found in their respective
documentations on the web and for \fluidpack{fft} and \fluidpack{sim} in the
two companion papers \citep[]{fluidfft, fluidsim}.
%
The code base was designed to follow Python 2.7 syntax during its genesis. Now,
it has been made forward compatible with Python 3 through the use of external
package \pack{future}.
%
We now tend to abandon Python 2.7 support for the next releases of the package.
%
This article will now focus on the base package \fluiddyn.

\subsection{API of the Python library \fluiddyn}

@@

\noindent\fbox{%
\begin{minipage}{0.97\textwidth}
  \codeinline{%
    (im1\_1.png, im1\_2.png, im1\_3.png, im2\_1.png, im2\_2.png, im2\_3.png)}
\end{minipage}
}

@@

\noindent\fbox{%
\begin{minipage}{0.55\textwidth}
\codeinline{((im1\_1.png, im1\_2.png, im1\_3.png),\\
  (im2\_1.png, im2\_2.png, im2\_3.png))}\\
\end{minipage}
}
\fbox{%
\begin{minipage}{0.385\textwidth}
\codeinline{((im1\_1.png, im2\_1.png),\\
  (im1\_2.png, im2\_2.png),\\
  (im1\_3.png, im2\_3.png))}
\end{minipage}
}
